Update and evaluation of the ozone dry deposition in the Oslo~CTM3 v1.0

### 2019-07-05 DryDep_supplement.tex
Edited section, added and updated plots using the actual drydep velos from output.
Finished first re-vision of sec. 3. Added subsection with comparison to MACC-reanalysis. But this might need to be revised.

\subsection*{S.6 Normalized zonal average ozone dry deposition velocity}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.55cm}]{pictures/final-norm_total_ozone_drydepvelo}
  \caption{Normalized zonal average ozone dry deposition velocity.}
\end{figure}

\subsection*{S.7 Surface resistance of ozone}
\begin{table*}[!htbp]
  \caption{Surface resistance of ozone $R^\chem{O_3}$ adapted from  Wesely (1989); Hough (1991): $^*$ CF -- temperate/boreal coniferous; DF -- temperate/boreal deciduous; NF -- Mediterranean needleleaf; BF -- Mediterranean broadleaf; TC -- temperate crop; MC -- Mediterranean crop; RC -- root crop; SNL -- moorland; GR -- grass; MS -- Mediterranean shrub; WE -- wetlands; TU -- tundra; DE -- desert; W -- water; ICE -- ice.}
  \begin{tabular}{lc}
    \tophline
    Code$^*$ & $R_\chem{O_3}$\\
         & (\unit{s\,m^{-1}})\\
    \middlehline
    CF, DF, NF, BF &  1000\\
    TC &  200 \\
    SNL, WE, U & 400 \\
    GR, MS  & 1000 \\
    TU, DE  & 385 \\
    W, ICE  & 1430 \\
    \bottomhline
 \end{tabular}
  %\belowtable{}
\end{table*}
\end{document}

>>>>

\subsection*{S.6 Normalized zonal average ozone dry deposition velocity}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.55cm}]{pictures/final-norm_total_ozone_drydepvelo_v2}
  \caption{Normalized zonal average ozone dry deposition velocity.}
\end{figure}

\subsection*{S.7 Surface resistance of ozone}
\begin{table*}[!htbp]
  \caption{Surface resistance of ozone $R^\chem{O_3}$ adapted from  Wesely (1989); Hough (1991): $^*$ CF -- temperate/boreal coniferous; DF -- temperate/boreal deciduous; NF -- Mediterranean needleleaf; BF -- Mediterranean broadleaf; TC -- temperate crop; MC -- Mediterranean crop; RC -- root crop; SNL -- moorland; GR -- grass; MS -- Mediterranean shrub; WE -- wetlands; TU -- tundra; DE -- desert; W -- water; ICE -- ice.}
  \begin{tabular}{lc}
    \tophline
    Code$^*$ & $R_\chem{O_3}$\\
         & (\unit{s\,m^{-1}})\\
    \middlehline
    CF, DF, NF, BF &  1000\\
    TC &  200 \\
    SNL, WE, U & 400 \\
    GR, MS  & 1000 \\
    TU, DE  & 385 \\
    W, ICE  & 1430 \\
    \bottomhline
 \end{tabular}
  %\belowtable{}
\end{table*}

\subsection{S.8 Comparison with MACC-reanalysis}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.5\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.55cm}]{pictures/annual_mean_surface_ozone_2005_Wesely_type}
  \caption{Mean ozone concentrations for the year 2005. (a) MACC-reanalysis (surface); (b) Oslo~CTM3 \emph{Wesely\_type} (lowermost model level); (c) Relative difference.}
\end{figure}

\end{document}
